---
title: "Gene Tree Species Tree"
output: html_document
---
Frst, get a tree from Open Tree of Life. We’ll get a recent plant tree from Beaulieu et al:

```{r}
library(rotl)
library(ape)
phy <- get_study_tree("ot_485", "tree1")
plot(phy, cex=0.3)
```

Let’s simplify by dropping some taxa:
```{r}
library(geiger)
phy <- drop.random(phy, Ntip(phy) - 10)
plot(phy)
axisPhylo()
```

We can simulate gene trees on this tree:
```{r}
library(phybase)
gene.tree <- phybase::sim.coaltree.phylo(phy, pop.size=1e-12)
plot(gene.tree)
```

And it probably looks very similar to the initial tree:
```{r}
library(phytools)
plot(cophylo(phy, gene.tree, cbind(sort(phy$tip.label), sort(gene.tree$tip.label))))
```

Make the branches short and fat:
```{r}
species.tree <- rcoal(7)
species.tree$edge.length <- species.tree$edge.length / (10*max(branching.times(species.tree)))
gene.tree <- phybase::sim.coaltree.phylo(species.tree)
plot(cophylo(species.tree, gene.tree, cbind(sort(species.tree$tip.label), sort(gene.tree$tip.label))))
```

You should see (in most iterations), the above code giving a mismatch between the gene tree and the species tree (the species tree has little height). Now, let’s lengthen the tips of the species tree:
```{r}
tip.rows <- which(species.tree$edge[,2]<=Ntip(species.tree))
species.tree2 <- species.tree
species.tree2$edge.length[tip.rows] <- 100 + species.tree2$edge.length[tip.rows]
gene.tree2 <- phybase::sim.coaltree.phylo(species.tree2)
plot(cophylo(species.tree2, gene.tree2, cbind(sort(species.tree2$tip.label), sort(gene.tree2$tip.label))))
```

It looks like a mismatch, but it’s hard to see, since the tips are so long. So plot the cladogram instead [we need to manually change branch lengths to do this, though note we do not resimulate the gene tree].
```{r}
species.tree2.clado <- compute.brlen(species.tree2)
gene.tree2.clado <- compute.brlen(gene.tree2)
plot(cophylo(species.tree2.clado, gene.tree2.clado, cbind(sort(species.tree2.clado$tip.label),
sort(gene.tree2.clado$tip.label))))
```